VOI-aware Monte-Carlo Sampling in Trees

### 2011-12-18 paper/vago/paper.tex
changes of eyal, but safek

\documentclass{article}
\usepackage{algpseudocode}
\usepackage[ruled]{algorithm}
\usepackage{url}
\usepackage{framed}
\usepackage{amsfonts,amsmath,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}
\usepackage{geometry}

@@

To estimate the VOI of pulling an arm, either a certain distribution
of the rewards should be assumed (and updated based on observed
rewards), or a distribution-independent bound on the VOI can be used
as the VOI estimate. In this paper, we use {\em concentration
  inequalities} to derive distribution-independent bounds on the VOI.

>>>>

\documentclass{article}
\usepackage{enumerate}
\usepackage{algpseudocode}
\usepackage[ruled]{algorithm}
\usepackage{url}
\usepackage{framed}
\usepackage{amsfonts,amsmath,amsthm,amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}
\usepackage{geometry}

@@

In order to estimate the VOI of pulling an arm, a sampling model is needed.
The generic sampling model used is: the actual value of an arm has a certain distribution.
Pulling an arm is an i.i.d. noisy measurement of the actual value of the arm.
In \cite{HayRussell.MCTS}, Section 4, two instances of this model are
examined:
\begin{enumerate}[a)]
\item uniformly distributed prior of the value, with Bernouli
  sampling, and 
\item normally distributed prior of the value, with normally
  distributed sampling.
\end{enumerate}

Here we examine the same general setting (i.i.d. samples), but instead
of using a specific distribution model, use {\em concentration
  inequalities} to derive distribution-independent bounds on the
VOI. Our bounds are applicable to any distribution that conforms to
our assumptions, including the case of normally distributed prior of
the value, with normally distributed sampling.
